Assessing the Scientific Value of Amateur Photometric Observations of Binary Star Transits

### 2025-01-05 paper.tex
docs: refactor and improvements
Signed-off-by: Thomas Mauran <thomasmauran@yahoo.com>

% Problematic
\subsection{Problematic}

% bold 
\textbf{How do amateur photometric observations of binary star transits compare in precision and reliability to data collected by professional astronomers, and is this collected data precise enough to contribute to science?}

@@

@@

In other words, during the transit, U Cephei will be 10 times less bright than when it's not in transit. This is a huge variation and makes it easier to detect the transit.

@@

% Methodology
\section{Methodology}
To address the research question, this study employs a comparative analysis of photometric data. Observations of the U Cephei binary star system were conducted using personal equipment under urban light pollution conditions (Bortle 7). The following steps were undertaken:
\begin{enumerate}
    \item Setup of observation equipment, including a CCD camera and a telescope with an aperture suitable for photometric studies.
    \item Observation of the U Cephei binary system taking 15 second exposure every 2 minutes.
    \item Acquisition of professional data on U Cephei from observatory archives and published studies for comparison.
    \item Standardization of data formats for comparative analysis.
    \item Statistical evaluation of precision, including signal-to-noise ratios and error margins.
    \item Reliability assessment through consistency checks and cross-validation with established models.
\end{enumerate}

% Equipment
\subsection{Equipment used}
Specifying the equipment used in the study is essential to understanding the context and limitations of the observations. 
I employed the following equipment for the photometric observations of U Cephei:

\begin{itemize}
    \item Telescope: Sky-Watcher Quattro 150P Newtonian reflector telescope with a 150mm aperture and 600mm focal length.
    \item Reducer: Sky-Watcher 0.85x Coma Corrector lowering the focal length to 510mm.
    \item Camera: ZWO ASI 585MC pro monochrome CCD camera with a 8.29 MP sensor.
    \item Filters: UV and IR cut filter for reducing light pollution and enhancing contrast.
    \item Mount: Celestron Celestrong cg-5 goto equatorial mount for trackin.
    \item Autoguider: ZWO ASI 120MM mini monochrome camera and 50mm guide scope for guiding.
    \item Software: N.I.N.A for image acquisition and PHD2 guiding software for tracking. AstroImageJ for data analysis.
    \item Light Pollution: Montpellier, Bortle 7 (suburban/urban transition) location with moderate light pollution.
\end{itemize}

\subsection{Cleaning the data}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{assets/aligned.png}
    \caption{Cleaned data of U Cephei.}
    \label{fig:cleaned_data}
\end{figure}

Here is an example aligned image after the Siril process, we can see that the software shifted
the frame to align the star in the sme way on all the images. During the process,
each image had to be debayered before being aligned, this process is called preprocessing.

@@

@@

\subsection{Conclusion}

@@

>>>>

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=1\textwidth]{assets/star-transits.jpg}
    \caption{Transit of binary star system schema and associated light curves.}
    \label{fig:transits}
\end{figure}

@@

In other words, during the transit, U Cephei will be 10 times dimmer than when it's not in transit. This is a huge variation and makes it easier to detect the transit.

@@

% Methodology
\section{Methodology}
To address the research question, this study employs a comparative analysis of photometric data. Observations of the U Cephei binary star system were conducted using personal equipment under urban light pollution conditions (Bortle 7). The following steps were undertaken:

\subsection{Observation Setup}

Specifying the equipment used in the study is essential to understanding the context and limitations of the observations. 
I employed the following equipment for the photometric observations of U Cephei:

\begin{itemize}
    \item Telescope: Sky-Watcher Quattro 150P Newtonian reflector telescope with a 150mm aperture and 600mm focal length.
    \item Reducer: Sky-Watcher 0.85x Coma Corrector lowering the focal length to 510mm.
    \item Camera: ZWO ASI 585MC pro monochrome CCD camera with a 8.29 MP sensor.
    \item Filters: UV and IR cut filter for reducing light pollution and enhancing contrast.
    \item Mount: Celestron Celestrong cg-5 goto equatorial mount for trackin.
    \item Autoguider: ZWO ASI 120MM mini monochrome camera and 50mm guide scope for guiding.
    \item Software: N.I.N.A for image acquisition and PHD2 guiding software for tracking. AstroImageJ for data analysis and Siril for aligning the images.
    \item Light Pollution: Montpellier, Bortle 7 (suburban/urban transition) location with moderate light pollution.
\end{itemize}

\subsection{Observation Procedure}

\subsection{Cleaning the amateur data}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=1\textwidth]{assets/aligned.png}
    \caption{Cleaned data of U Cephei and it's comparison stars used for the study.}
    \label{fig:cleaned_data}
\end{figure}

Here is an example aligned image after the Siril process, we can see that the software shifted
the frame to align the star in the same way on all the images. During the process,
each image had to be debayered before being aligned, this process is called preprocessing.

@@

\subsection{Professional Data Acquisition}

\subsection{Standardization of Data Formats, light curves and comparative analysis}

@@

@@

\section{Discussion}
